### 2024-08-14 cluster-analysis.qmd
20240813 - move processing earlier

```{r}
merged_data <- merged_data %>% 
  separate(ht, into = c("feet", "inches"), sep = "-") %>%
  mutate(
    feet = as.numeric(feet),
    inches = as.numeric(inches),
    ht_numeric = feet * 12 + inches
  ) %>%
  select(-feet, -inches)

merged_data <- merged_data %>% 
  mutate(
    height_coalesced = coalesce(height, ht_numeric),
    weight_coalesced = coalesce(weight, wt),
    receptions_coalesced = pmax(receptions, rec.rec, na.rm = TRUE),
    receiving_air_yards_per_rec = receiving_air_yards / receptions
  )

>>>>

```{r}
merged_data <- merged_data %>% 
  mutate(
    height_coalesced = coalesce(height, ht_numeric),
    weight_coalesced = coalesce(weight, wt),
    receptions_coalesced = pmax(receptions, rec.rec, na.rm = TRUE),
    receiving_air_yards_per_rec = receiving_air_yards / receptions
  )

### 2024-08-14 download-football-data.qmd
20240813 - move processing earlier

```{r}
# Drop Stanford Samuels Jr.
nfl_combine$gsis_id[which(nfl_combine$cfb_id == "stanford-samuels-1")] <- NA
```

>>>>

```{r}
# Drop Stanford Samuels Jr.
nfl_combine$gsis_id[which(nfl_combine$cfb_id == "stanford-samuels-1")] <- NA

nfl_combine <- nfl_combine %>% 
  separate_wider_delim(
    ht,
    names = c("feet", "inches"),
    delim = "-") %>%
  mutate(
    feet = as.numeric(feet),
    inches = as.numeric(inches),
    ht = feet * 12 + inches
  ) %>%
  select(-feet, -inches)
```
